Sparse Function-space Representation \\ of Neural Networks

### 2023-05-17 paper/main.tex
toy examples

\paragraph{Toy examples} For illustrative purposes, we smoke-test our approach on a 1D regression problem (\cref{fig:teaser}) and on the 2D Banana classification task (\cref{fig:banana}). In \cref{fig:teaser}, we train an MLP neural network with two hidden layers (64 hidden units each, tanh activation). The middle panel shows the \our result on a sparse set of data examples, while the rightmost panel demonstrates fast dual conditioning on new data (from \cref{sec:sequential}). In \cref{fig:banana}, we use an MLP with two hidden layers (64 units, sigmoid) and compare to the HMC result obtained by hamiltorch \cite{cobb:} (10~chains, 10,000 samples).

@@

>>>>

\paragraph{Toy examples} For illustrative purposes, we smoke-test our approach on a 1D regression problem (\cref{fig:teaser}) and on the 2D Banana classification task (\cref{fig:banana}). In \cref{fig:teaser}, we train an MLP neural network with two hidden layers (64 hidden units each, tanh activation). The middle panel shows the \our result on a sparse set of data examples, while the rightmost panel demonstrates fast dual conditioning on new data (from \cref{sec:sequential}). In \cref{fig:banana}, we use an MLP with two hidden layers (64 units, sigmoid) and compare to the HMC result obtained by hamiltorch \cite{cobb2020scaling} that shows capture similar behaviour as HMC.

@@

\begin{table}[t!] 
  \centering\scriptsize
  \caption{Negative log predictive density (NLPD) (lower better) for SVGP (sparse GP mean and variance), SVGP NN (NN mean and sparse GP variance), GP subset (subset GP mean and variance) and GP NN subset (NN mean and GP subset variance) for inducing points in $[16, 32, 64, 128, 256]$. } 
	\label{tbl:uci}
	% Control table spacing
	\renewcommand{\arraystretch}{1.}
	\setlength{\tabcolsep}{2pt}
	\setlength{\tblw}{0.14\textwidth}

    % THE TABLE NUMBER ARE GENERATED BY A SCRIPT	
	\input{tables/uci_all.tex}
\end{table}
